Titeln på avhandlingens språk

### 2022-12-11 body/part1/overview.tex
writing

\begin{figure}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{Figs/trace_edgedroid.png}
        \caption{%
            High level conceptual design of our methodology for \ac{WCA}.
            We replace the human by a trace-driven emulation.
            This allows us to maintain realism in inputs sent over the network to the compute process on the backend, while simplifying the design of the client software.
        }
    \end{subfigure}
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \adjustbox{scale=0.75}{
            \begin{tikzpicture}[align=center,
            node distance=.5cm and 1.5cm,
            every initial by arrow/.style={-{Latex[length=2mm]}}]
            % Place nodes              
            \node [initial, state, minimum size=6em, initial text=] (play) {Play};               
            \node [state, above right=of play, minimum size=6em] (change) {Change\\step};
            \node [state, below right=of play, minimum size=6em] (rewind) {Rewind};
            \node [state, accepting, above right=of rewind, minimum size=6em] (shutdown) {Shutdown};

@@

            \end{tikzpicture}
        }
        \caption{State diagram of the user model governing the replay of the pre-recorded trace at runtime.}\label{fig:usermodel}
    \end{subfigure}
    \caption{%
        Overview of our first implementation of the methodology for \ac{WCA}.
    }\label{fig:edgedroid1:trace}
\end{figure}

@@

The overall goal of these papers is to explore this methodological approach as applied to \ac{WCA}.
For this purpose, we introduce a tool, \emph{EdgeDroid 1.0}, which mimics the behavior of a human interacting with a \ac{WCA} client application.

To establish a reproducible and comparable workload, we use a trace-based design for the client-side emulation.
We first record a trace of the sensory input data while having a human user operate the target application.
The collected data consists of the sensory inputs provided to the system at runtime, for instance --- in the case of a video-based application --- the video feed from the camera.

@@

\begin{figure}
    \centering%
    \includegraphics[width=.85\columnwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/rtt_fb_vs_nofb}%
    \caption{Comparison of round-trip-times for inputs that triggered a state transition in the task model versus inputs that did not.}%
    \label{fig:comparison:rtt}%
\end{figure}%
\begin{figure}
    \centering%
    \includegraphics[width=.85\columnwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_feedback}%
    \caption{Distribution of latency across system components for inputs that triggered a state transition in the task model.}%
    \label{fig:comparison:feedback}%
\end{figure}%
\begin{figure}%
    \centering%
    \includegraphics[width=.85\columnwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_taskstep}%
    \caption{Round-trip-times for input-feedback cycles associated with state transitions in the internal task model for a single client connected over an optimal wireless link.}%
    \label{fig:comparison:tasksteps}
\end{figure}%

@@

\begin{figure}
    \centering
    \includegraphics[width=.6\columnwidth]{publications/2022CLEAVE/images/inverted_pendulum.png}
    \caption{
        The 2D inverted pendulum system.
    }\label{fig:invpend}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Principal Component Analysis}\label{tab:pca}
    \begin{subtable}[h]{\textwidth}
        \centering
        \caption{Main components identified.}
        \setlength{\tabcolsep}{0pt} % let TeX compute the intercolumn space
        \begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}\quad}lrrr@{}}
            \toprule
            \textbf{Factor} & \textbf{Comp. 1} & \textbf{Comp. 2} & \textbf{Comp. 3} \\
            \midrule
            BFI Conscientiousness                  & \textcolor{lightgray}{\( -0.022 \)} &                         \( 0.668 \) & \textcolor{lightgray}{\( -0.481 \)} \\
            BFI Neuroticism                        &                         \( 0.600 \) &                        \( -0.678 \) & \textcolor{lightgray}{\( -0.118 \)} \\
            ITQ Focus                              &                         \( 0.678 \) &  \textcolor{lightgray}{\( 0.203 \)} &                         \( 0.504 \) \\
            ITQ Involvement                        &                         \( 0.573 \) &                         \( 0.540 \) &  \textcolor{lightgray}{\( 0.417 \)} \\
            Exec. Time (delay 3.0 s, length 12)    &                         \( 0.758 \) & \textcolor{lightgray}{\( -0.178 \)} & \textcolor{lightgray}{\( -0.348 \)} \\
            Log EEG power \( \alpha + \beta \) Slice 1 & \textcolor{lightgray}{\( -0.436 \)} & \textcolor{lightgray}{\( -0.251 \)} &                         \( 0.589 \) \\
            \bottomrule
        \end{tabular*}
    \end{subtable}
    \newline
    \medskip
    \newline
    \begin{subtable}[h]{\textwidth}
        \centering
        \caption{Percentages of variance explained by the components.}
        \begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}\quad}lrrrr@{}}
            \toprule
            {} & \textbf{Comp. 1} & \textbf{Comp. 2} & \textbf{Comp. 3} & \textbf{Total} \\
            \midrule
            Explained Variance & \SI{31.88}{\percent} & \SI{22.22}{\percent} & \SI{19.03}{\percent} & \SI{73.13}{\percent} \\
            \bottomrule
        \end{tabular*}
    \end{subtable}
\end{table}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{.47\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figs/trace_edgedroid.png}
        \caption{%
            High level conceptual design of our methodology for \ac{WCA}.
            We replace the human by a trace-driven emulation.
            This allows us to maintain realism in inputs sent over the network to the compute process on the backend, while simplifying the design of the client software.
        }
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{.47\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2018DemoScalingOnTheEdge/img/TraceReplay_GenArch}
        \caption{%
            Architectural overview of the EdgeDroid \num{1.0} tool.
            The ``client emulator app'' implements the aforementioned user model together with the required networking functionality to connect to a \ac{WCA} backend running on a cloudlet.%
            }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \adjustbox{scale=0.7}{
            \begin{tikzpicture}[align=center,
            node distance=.5cm and 1.5cm,
            every initial by arrow/.style={-{Latex[length=2mm]}}]
            % Place nodes              
            \node [initial, state, minimum size=6em, initial text=] (play) {Play};               
            \node [state, above right=of play, minimum size=6em] (change) {Change\\step};
            \node [state, below right=of play, minimum size=6em] (rewind) {Rewind};
            \node [state, accepting, above right=of rewind, minimum size=6em] (shutdown) {Shutdown};

@@

            \end{tikzpicture}
        }
        \caption{State diagram of the user model governing the replay of the pre-recorded trace at runtime. This model approximates the behavior of an ``ideal'' human, one that is patient and makes no mistakes.}\label{fig:usermodel}
    \end{subfigure}
    \caption{%
        Overview of our first implementation of the methodology for \ac{WCA}.
    }\label{fig:edgedroid1:trace}
\end{figure}

@@

The overall goal of these papers is to explore this methodological approach as applied to \ac{WCA}.
As discussed in \cref{chap:introduction}, the main challenge to benchmarking \ac{WCA} --- and other ``human-in-the-loop'' applications on the edge --- concerns the involvement of human beings in their operation.
Humans are unreliable, and, perhaps more importantly, hard to scale.
\todo[inline]{More reasons}

The implementation of the client-side emulation necessary for our methodology follows in these works a trace-based design.
We introduce a tool, \emph{EdgeDroid \num{1.0}}, which replays a pre-recorded trace of sensory inputs to the original \ac{WCA} backend.
The tool is implemented in Android, allowing for its easy deployment on the same kind of \ac{COTS} mobile devices on which real \ac{WCA} applications are intended to run in the future.
Furthermore, this tool is instrumented, allowing us to collected a multitude of system-level metrics at runtime which can then be analyzed.
On the other hand, the trace in question corresponds to a pre-recorded sequence of sensory inputs obtained from a real execution of the \ac{WCA} by a human volunteer.
The trace is recorded in a near-ideal setting, such that it does not include either human mistakes or segments with degraded system responsiveness.
Once recorded, the trace is manually segmented into the logical component steps of the task, and these are replayed in sequence back to the backend by the EdgeDroid tool.

Utilizing a trace for the emulation of human behavior in \ac{WCA} has multiple advantages.
The first of these is the level of realism if affords in terms of the payloads sent over the network and, in particular, processed by the backend.
Using a trace ensures that the same computation is performed on the edge as if a human was involved, while also ensuring a reproducible application execution path.
The second is simplicity, as such an approach does not require complex modeling of human behavioral patterns, merely the observation and recording of them.
The third is extensibility.

\todo[]{}

reproducible and comparable workload, we use a trace-based design for the client-side emulation.
.

@@

\begin{figure}
    \centering%
    \includegraphics[width=.85\textwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/rtt_fb_vs_nofb}%
    \caption{Comparison of round-trip-times for inputs that triggered a state transition in the task model versus inputs that did not.}%
    \label{fig:comparison:rtt}%
\end{figure}%
\begin{figure}
    \centering%
    \includegraphics[width=.85\textwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_feedback}%
    \caption{Distribution of latency across system components for inputs that triggered a state transition in the task model.}%
    \label{fig:comparison:feedback}%
\end{figure}%
\begin{figure}%
    \centering%
    \includegraphics[width=.85\textwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_taskstep}%
    \caption{Round-trip-times for input-feedback cycles associated with state transitions in the internal task model for a single client connected over an optimal wireless link.}%
    \label{fig:comparison:tasksteps}
\end{figure}%

@@

\begin{figure}
    \centering
    \includegraphics[width=.6\textwidth]{publications/2022CLEAVE/images/inverted_pendulum.png}
    \caption{
        The 2D inverted pendulum system.
    }\label{fig:invpend}
\end{figure}

@@

\begin{table}[h]
    \centering
    \caption{Principal Component Analysis}\label{tab:pca}
    \begin{subtable}[h]{\textwidth}
        \centering
        \caption{Main components identified.}
        \setlength{\tabcolsep}{0pt} % let TeX compute the intercolumn space
        \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}\quad}lrrr@{}}
            \toprule
            \textbf{Factor} & \textbf{Comp. 1} & \textbf{Comp. 2} & \textbf{Comp. 3} \\
            \midrule
            BFI Conscientiousness                  & \textcolor{lightgray}{\( -0.022 \)} &                         \( 0.668 \) & \textcolor{lightgray}{\( -0.481 \)} \\
            BFI Neuroticism                        &                         \( 0.600 \) &                        \( -0.678 \) & \textcolor{lightgray}{\( -0.118 \)} \\
            ITQ Focus                              &                         \( 0.678 \) &  \textcolor{lightgray}{\( 0.203 \)} &                         \( 0.504 \) \\
            ITQ Involvement                        &                         \( 0.573 \) &                         \( 0.540 \) &  \textcolor{lightgray}{\( 0.417 \)} \\
            Exec. Time (delay 3.0 s, length 12)    &                         \( 0.758 \) & \textcolor{lightgray}{\( -0.178 \)} & \textcolor{lightgray}{\( -0.348 \)} \\
            Log EEG power \( \alpha + \beta \) Slice 1 & \textcolor{lightgray}{\( -0.436 \)} & \textcolor{lightgray}{\( -0.251 \)} &                         \( 0.589 \) \\
            \bottomrule
        \end{tabular*}
    \end{subtable}
    \newline
    \medskip
    \newline
    \begin{subtable}[h]{\textwidth}
        \centering
        \caption{Percentages of variance explained by the components.}
        \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}\quad}lrrrr@{}}
            \toprule
            {} & \textbf{Comp. 1} & \textbf{Comp. 2} & \textbf{Comp. 3} & \textbf{Total} \\
            \midrule
            Explained Variance & \SI{31.88}{\percent} & \SI{22.22}{\percent} & \SI{19.03}{\percent} & \SI{73.13}{\percent} \\
            \bottomrule
        \end{tabular*}
    \end{subtable}
\end{table}
